Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-21 article.tex
Reproducibility: mention SBML test suite

To evaluate SimBio's reproducibility, we analyzed curated \ac{SBML} models
from BioModels \cite{malik-sheriffBioModels15Years2020}. Among the first 100 curated
models from BioModels we selected 60 that did not contains events, as
SimBio doesn't support events yet. We simulated the selected models with
COPASI and used the simulated results as ground truth, and demonstrated
that SimBio reproduces the results with minor numerical differences
depending on the solver tolerance.

For performance testing, we ran simulations using COPASI,
Tellurium/RoadRunner, and SimBio. Within SimBio, both NumPy and Numba
backends were considered. The LSODA solver was used for COPASI and
SimBio, while for Tellurium the comparable CVODE solver was used. In all
cases, we used relative and absolute tolerances of \(10^{-6}\). We
measured three simulation stages: loading, the initial (cold) run, and
subsequent (warm) runs for each model.

>>>>

To evaluate SimBio's reproducibility,
we used the \ac{SBML} test suite \cite{SBMLTestSuite},
which provides a set of \ac{SBML} models
and the expected result of a simulation.
Excluding models that use not yet supported \ac{SBML} feature,
every simulation returned correct results within the solver tolerances.

To evaluate SimBio's performance,
we used curated \ac{SBML} models from BioModels \cite{malik-sheriffBioModels15Years2020}.
Among the first 250 curated models,
we considered the 117 that used supported \ac{SBML} features.
We ran simulations using COPASI, Tellurium/RoadRunner, and SimBio.
Within SimBio, both NumPy and Numba
backends were considered.
The LSODA solver was used for COPASI and SimBio,
while for Tellurium the comparable CVODE solver was used.
In all cases, we used relative and absolute tolerances of \(10^{-6}\).
We measured three simulation stages:
loading, the initial (cold) run, and subsequent (warm) runs for each model.
